---
title: "p8105_hw1_jz3573"
output: html_document
date: "September 23,2023"
---

# Problem 1
This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.

#### Setup & Have an overview of the variable

```{r setup & overview of the variable }
library(moderndive)
data("early_january_weather")
early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```
There are 15 variables in this dataset, including origin, year, month, day, hour, temp, dewp, humid, wind_dir,wind_speed, wind_gust,precip, pressure, visib, and time_hour.

1 varible is character: Origin;  3 varibles are integer: year, month, day, hour; 9 variables are double-precision(with 2 decimal values): temp, dewp, humid, wind_dir,wind_speed, wind_gust,precip, pressure, visib; 1 variable is dates and times: time_hour

There are 358 rows and 15 columns in this dataset. 

The mean temperature is 39.58212

#### Make a scatterplot 
```{r make a scatterplot}
library(tidyverse)
ggplot(early_january_weather,aes(x=time_hour, color=humid, y=temp))+geom_point()
```
The average temperature and humid is getting higher as time goes by, but these positive relationships fluctuate. 

#### Save the scatterplot 
```{r save the scatterplot}
ggsave("temp_humid_time.png")
```

# Problem 2
This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

#### Create a dataframe

```{r create a dataframe}
df=tibble(
  vec_num=rnorm(10,sd=1),
  vec_logic=vec_num>0,
  vec_char=c("today","is","rainy","continously", "My","shirt","and", "pants", "get","wet"),
  vec_factor=factor(c("red","blue","green","red","green","blue","blue","green","red","green"))
)
```


#### Take the mean of each variables

```{r take the mean }
mean(pull(df,vec_num))
mean(pull(df,vec_logic))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))
```
Numeric and logical variables have means. Character and factor variables cannot be taken for mean. 

####  Convert logic,charater and factor variables into numeric variables

```{r convert into numeric, eval=FALSE}
as.numeric(pull(df,vec_logic))
as.numeric(pull(df,vec_char))
as.numeric(pull(df,vec_factor))
```

The factor variable, color, and the logic variable can be converted into number, and characters variable cannot be converted into number in this way. As a result, "mean" function can take the mean of logic variables. And after factor variable,color, being converting into numeric variables using as.numeric, it can also have a mean, as shown below. 

```{r  }
mean(as.numeric(pull(df,vec_factor)))
