---
title: "p8105_hw1_jz3573"
output: html_document
date: "September 23,2023"
---

# problem 1

```{r setup & overview of the variable }
library(moderndive)
data("early_january_weather")
early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```
There are 15 variables in this dataset, including origin, year, month, day, hour, temp, dewp, humid, wind_dir,wind_speed, wind_gust,precip, pressure, visib, and time_hour.

1 varible is character: Origin;  3 varibles are integer: year, month, day, hour; 9 variables are double-precision(with 2 decimal values): temp, dewp, humid, wind_dir,wind_speed, wind_gust,precip, pressure, visib; 1 variable is dates and times: time_hour

There are 358 rows and 15 columns in this dataset. 

The mean temperature is 39.58212

```{r make a scatterplot}
library(tidyverse)
ggplot(early_january_weather,aes(x=time_hour, color=humid, y=temp))+geom_point()
```
The average temperature and humid is getting higher as days go by, but the relationship fluctuates. 

```{r save the scatterplot}
ggsave("temp_humid_time.png")

